Multi-modality Imagery Database for Plant Phenotyping

### 2015-04-24 datapaper.tex
Xi_baseline
update section 1-3 by jc

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{multirow}
\usepackage{tabularx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

\subsection{Image Acquisition}

\subsection{Image Calibration}

\subsection{Creative Senz3D}

The depth and color images were collected using a Creative Senz3D sensor.
This section describes characterizes the data from this sensor, particularly the depth data.
The sensor contains both a $1280 \times 720$ color camera directed parallel to, and separated by roughly 25 mm from, a depth camera which has resolution of $320\times240$ pixels.
The depth sensor uses a flash near IR illuminator and measures the time-of-flight of the beam at each pixel to obtain dense depth estimates along with an IR reflectance at each pixel.

There are a number of limitations to the depth sensor including sources of depth error.  The primary measurement limit on the range-to-target is the strength of the reflected beam. Hence dark, matt surfaces are measured reliably only at close range on the order of 20 or 30cm.  Highly reflective surfaces also pose problems with direct reflections leading to saturation and highly unreliable depths.  In addition reflective surfaces at grazing angles are less reliably measured as little signal is reflected.  Hence in our data portions of the chamber floor visible in Fig.~\ref{fig:CameraConfiguration} are highly reflective and have incorrect depths.  Fortunately the primary goal of the depth measurements are to obtain leaf depths, and plants provide good, roughly Lambertian reflections of IR~\cite{Chelle2006219}.  Thus For these reasons the non-leaf depth pixels in the 3D data are unreliable and should be ignored.  Another limitation is that the IR illuminator is slightly offset on the left of the sensor and this results in shadows to the right of some objects, as well as mixed pixels on depth discontinuities.  Both of these can be readily detected as large standard deviations in the depth image.

\subsubsection{Sensor Calibration}

@@

\subsubsection{Data Description}

The data consist of 5 images per hour taken within 10 minutes of each other.  These include the fluorescent image, the IR reflectance image with the same camera, the color image, the 3D-depth and a confidence image.  The 3D-depth image is built from the depth sensor by transforming the points into world coordinates and is expressed in mm.  The confidence image is the standard deviation of the depths pixels.  This is useful for identifying pixels at depth discontinuities which are unreliably detected and result in large standard deviations.  In addition pixels with no response and saturated pixels are given the maximum standard deviation, and should be filtered out.

\subsection{Image Accusation}

\subsection{Image Calibration}

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{bm}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{multirow}
\usepackage{tabularx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

%\subsection{Image Acquisition}

\subsection{Sensor Calibration}

@@

%\subsubsection{Data Description}

%\subsection{Image Accusation}

%\subsection{Image Calibration}

### 2015-04-24 datapaper_hardware.tex
update section 1-3 by jc

Chlorophyll a fluorescence images were captured once per hour during the daylight period in a DEPI chamber [CITE].  A set of 5 images (for averaging) were captured using a Hitachi KP-F145GV CCD (Hitachi Kokusai Electric America Inc., Woodbury, NY)  camera outfitted with an infrared long pass filter (Schott Glass RG-9, Thorlabs, Newton, NJ), during a short period ($<400 msec$) of intense light saturating to photosynthesis ($>10,000 \mu mol~photons~m^{-2} s^{-1}$) provided by an array of white Cree LEDs (XMLAWT, 5700K color temperature, Digi-Key, Thief River Falls, MN) collimated using a 20mm Carclo Lens (10003, LED Supply, Lakewood, CO).
%
Chlorophyll a fluorescence was excited using monochromatic red LEDs (Everlight 625nm, ELSH-F51R1-0LPNM-AR5R6, Digi-Key), collimated using a Ledil reflector optic ($C11347\_REGINA$, Mouser Electronics, Mansfield, TX) and pulsed for $50 \mu s$ during a brief window when the white LEDs were electronically shuttered.  A series of 5 images were also collected in the absence of excitation light for artifact subtraction.

@@

[cite]Cruz, J.A. et al. Dynamic Environmental Photosynthetic Imaging (DEPI) Reveals Emergent Phenotypes Related to the Environmental Repsonses of Photosynthesis. Nature Biotechnology Submitted (2015).

>>>>

In this section, we introduce the hardware used for capturing Fluorescence, IR, RGB color, and depth imagery data.

\subsubsection{Fluorescence and IR images}
Chlorophyll a fluorescence images were captured once per hour during the daylight period in a growth chamber~\cite{cruz2015depi}. A set of 5 images were captured using a Hitachi KP-F145GV CCD camera (Hitachi Kokusai Electric America Inc., Woodbury, NY) outfitted with an infrared long pass filter (Schott Glass RG-9, Thorlabs, Newton, NJ), during a short period ($<400 msec$) of intense light saturating to photosynthesis ($>10,000 \mu mol~photons~m^{-2} s^{-1}$) provided by an array of white Cree LEDs (XMLAWT, 5700K color temperature, Digi-Key, Thief River Falls, MN) collimated using a 20mm Carclo Lens (10003, LED Supply, Lakewood, CO).
%
Chlorophyll a fluorescence was excited using monochromatic red LEDs (Everlight 625nm, ELSH-F51R1-0LPNM-AR5R6, Digi-Key), collimated using a Ledil reflector optic ($C11347\_REGINA$, Mouser Electronics, Mansfield, TX) and pulsed for $50 \mu s$ during a brief window when the white LEDs were electronically shuttered.  A series of 5 images were also collected in the absence of excitation light for artifact subtraction.

@@

\subsubsection{RGB color and depth images} %This section describes characterizes the data from this sensor, particularly the depth data.

The depth and RGB color images were collected using a Creative Senz3D sensor~\cite{nguyen2015vietnamese}. The sensor contains both a $1280 \times 720$ color camera directed parallel to, and separated by roughly 25 mm from, a depth camera which has resolution of $320\times240$ pixels. The depth sensor uses a flash near IR illuminator and measures the time-of-flight of the beam at each pixel to obtain dense depth estimates along with an IR reflectance at each pixel.

There are a number of limitations to the depth sensor including sources of depth error. The primary measurement limit on the range-to-target is the strength of the reflected beam. Hence dark, matt surfaces are measured reliably only at close range on the order of $20$ or $30cm$.  Highly reflective surfaces also pose problems with direct reflections leading to saturation and highly unreliable depths.  In addition reflective surfaces at grazing angles are less reliably measured as little signal is reflected.  Hence in our data portions of the chamber floor visible in Fig.~\ref{fig:CameraConfiguration} are highly reflective and have incorrect depths.  Fortunately the primary goal of the depth measurements are to obtain leaf depths, and plants provide good, roughly Lambertian reflections of IR~\cite{Chelle2006219}.  Thus For these reasons the non-leaf depth pixels in the 3D data are unreliable and should be ignored.  Another limitation is that the IR illuminator is slightly offset on the left of the sensor and this results in shadows to the right of some objects, as well as mixed pixels on depth discontinuities.  Both of these can be readily detected as large standard deviations in the depth image.

The imagery data were collected once per hour. %taken within 10 minutes of each other.  %
These include the fluorescent image, the IR reflectance image with the same camera, the color image, the 3D-depth and a confidence image.  The 3D-depth image is built from the depth sensor by transforming the points into world coordinates and is expressed in mm.  The confidence image is the standard deviation of the depths pixels.  This is useful for identifying pixels at depth discontinuities which are unreliably detected and result in large standard deviations.  In addition pixels with no response and saturated pixels are given the maximum standard deviation, and should be filtered out.

### 2015-04-24 datapaper_intro.tex
update section 1-3 by jc

As the growing of population in the world and the reduction of arable land, there is an increasing desire to improve the yield and quality of various crops, where the undersanding of biology and mechanism of plant growth is a key enabler.
For this purpose, plant biologists create different mutations of the plant, grow them in either indoor chamber or outdoor field, visually observe them during the growth perid, and finally discover the patterns that associate the   key factors (e.g., genre, environments) with the outcome (e.g., visual phenotype, yield)~\cite{}.
While many factors in this research procedure can be assessed quantitatively, which is necessary in order to perform large-scale study, one of the bottleneck is the automatic visual phenotyping.

Plant phenotyping aims to analyze and categorize the visual appearance of plants~\cite{}.
This is typically conducted via manual visual observation.
With the increasing lower cost of imaging sensors and advances of Computer Vision technologies, image-based automatic plant phenotyping is growing into a desirable and viable solution~\cite{}.
In this interdisciplinary solution, computer vision scientists employ various imaging sensors to capture the plants and design advanced algorithms to automatically analyze the plant imagery, with the goal of answering the questions posed by plant biologists.

Plant image analysis is a non-trivial computer vision task, due to diverse variations of leaf appearance, overlapping and dynamics.
In order to develop advanced algorithms, image databases that are well representative of this application domain is highly important.
In fact, computer vision research lives on and advances with databases, as evidenced by the successful databases in the field (e.g., FERET~\cite{Phillips2000}, LFW~\cite{LFW}, Caltech$101$~\cite{Fei-Fei2004}).
However, the publicly available database on plant imagery is very limited, with the only exception of~\cite{scharr2014annotated} and~\cite{haug2014crop}.
Both databases have the limitations in that they only capture RGB images, and are suitable for a small set of tasks.

To facilite future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a newly collected multi-modality plant imagery database, termed ``MSU-PID''.
The MSU-PID includes the imagery of two types of plants (Arabidopsis and bean) captured by four types of sensors, Fluorescence, IR, RGB color, and depth.
All four sensors are synchonized to perform the data capturing periodically for multiple days. 
Checkerboard-based camera calibration is perform between the multiple sensors, which results in the explicit correspondence between the pixels of any two modalities.
For a subset of the database, we manually label the ground truth on the leaf identification number, leaf tip locations and leaf segments, using our labeling tool.
To provide a performance baseline for future comparison, we apply our automatic leaf segmentation approach~\cite{yin2014a,yin2014b} to the Arabidopsis imagery and demonstrate the challenge of image analysis on this database.

In summary, this paper and our database have made the following main contribution. 
\begin{itemize}
\item MSU-PID is the first {\it multi-modality} plant image database. 
This allows researchers to study the strength and weakness of individual modality, as well as their fusion in plant image analysis.
\item Our imaging setup and the variety of manu labele make MSU-PID a candidate dataset for a diverse set of plant image analysis tasks, including leaf segementation, leaf counting, leaf alignment, leaf tracking, leaf growth prediction, etc.
\end{itemize}

>>>>

With the rapid growth of world population  and the loss of arable land, there is an increasing desire to improve the yield and quality of crops, where the understanding of the genetic mechanisms to control plant growth is a key enabler~\cite{doos2002population}.
%
For this purpose, plant scientists make various genetic mutant strains of plants, grow them either in  growth chambers with simulated environmental conditions or directly in the field, visually observe the plants during the growth period, and finally discover plant morphological or physiological patterns that tightly associate with key growth factors~\cite{houle2010phenomics}.
%
While many factors can be assessed quantitatively, which is essential for high-throughput study, one of the bottleneck in this research line is plant visual phenotyping~\cite{walter2015plant}.

Plant visual phenotyping aims to analyze and categorize the visual appearance of plants~\cite{}. In old days, this was conducted via manual visual observation~\cite{Erblichkeit1903}. Today, with the increasing lower cost of imaging sensors and advances of computer vision technologies, image-based automatic plant visual phenotyping is growing into a desirable and viable solution~\cite{cruz2015depi}. In this interdisciplinary field, scientists employ various imaging sensors to capture plants and design advanced algorithms to automatically analyze the captured plant imagery, with the goal of raising testable biological hypotheses to solve the aforementioned problems.

Due to diverse variations of leaf appearance, layout, growth and movement, plant image analysis is a non-trivial computer vision task~\cite{}. In order to develop advanced algorithms, image databases that are well representative of this application domain is highly important. In fact, computer vision research lives on and advances with databases, as evidenced by the successful databases in the field (e.g., FERET~\cite{Phillips2000}, LFW~\cite{LFW}, Caltech$101$~\cite{Fei-Fei2004}). However, the publicly available database for plant phenotyping is still limited, with the only exception of LSC database \cite{scharr2014annotated}, which, nevertheless, has its own limitations on the type of images (RGB only), and is only suitable for a small set of applications.

To facilitate future research on plant image analysis, as well as remedy the limitation of existing databases in the field, this paper presents a newly collected multi-modality plant imagery database, termed ``MSU-PID''. The MSU-PID includes the imagery of two types of plants (Arabidopsis and bean), both are widely used in plant research, captured by four types of sensors, i.e. Fluorescence, IR, RGB color, and depth.
%
All four sensors are synchronized and are programmed to periodically capture data for multiple days. Checkerboard-based camera calibration is perform between the multiple sensors, which results in the explicit correspondence between the pixels of any two modalities. For a subset of the database, we manually label the ground truth on the leaf identification number, leaf tip locations and leaf segments. To provide a performance baseline for future comparison, we apply our automatic leaf segmentation approach~\cite{yin2014a,yin2014b} to the Arabidopsis imagery and demonstrate the challenge of image analysis on this database.

In summary, this paper and our database have made the following main contributions.
\begin{itemize}
\item MSU-PID is the first {\it multi-modality} plant image database. This allows researchers to study the strength and weakness of individual modality, as well as their fusion in plant image analysis.
\item Our imaging setup and the variety of manual label make MSU-PID an ideal candidate for evaluating a diverse set of plant image analysis tasks, including leaf segmentation, leaf counting, leaf alignment, leaf tracking, leaf growth prediction.
\end{itemize}

### 2015-04-24 datapaper_prior.tex
update section 1-3 by jc

Databases drive computer vision research.
Hence, it is always important to develop and promopt properly captured databases in the vision community.
While there is a clear desire to apply computer vision to plant imagery, the lack of databases is an obstacle for the further study and development.

 We summarize all existing publicly available databases that are related to plant imagery in Table~\ref{tab:database}.
In terms of potential applications of the databases, they can be categorized into two types.
The first type is for the general purpose of recognizing a particular species of tree or plant.
The Swedish leaf database~\cite{soderkvist2001computer} is probably the first leaf database even though the images are captured by scanners. 
The Flavia database~\cite{wu2007leaf} is consideraly larger and a neural network is used to train a leaf classifier.
The most recent leafsnap project is an impressive effort that includes a very large dataset of $184$ tree types~\cite{kumar2012leafsnap}.
A mobilephone app is also developed to make the leaf classification system portable.
Finally, the crop/weed image database~\cite{haug2014crop} is captured by a robot in the real field, and used for classifying crop vs.~weed.
Note that in this type of databases, normally only a single leaf is imaged and as a result, the challenging problem of leaf segmentation has been bypassed.

The second type of databases is for plant phenotyping where it is important to keep the plant live while imaged.
Thus, no destructive action is taken and an entire plant is imaged.
The LSC database~\cite{scharr2014annotated} is the most similar one to our database.
It captures a large set of RGB images for the Arabidopsis and Tobacco plants.
The provided manual labels allow the evaluation of leaf segmentation and leaf counting.
In comparison, our MSU-PID database utilizes four sensing modalities in the data capturing, each providing different aspects of plant appearance.
Our manual label also enable us to develop algorithm on additional applications such as leaf tracking and alignment.

>>>>

Databases drive computer vision research. Hence, it is always important to develop and promote properly captured databases in the vision community. While there is a clear desire to apply computer vision to plant imagery, the lack of databases is an obstacle for the further study and development.

We summarize all existing publicly available databases that are related to plant imagery in Table~\ref{tab:database}. In terms of potential applications of the databases, they can be categorized into two types. The first type is for the general purpose of recognizing a particular species of tree or plant. The Swedish leaf database~\cite{soderkvist2001computer} is probably the first leaf database even though the images are captured by scanners. The Flavia database~\cite{wu2007leaf} is considerably larger and a neural network is used to train a leaf classifier. The most recent leafsnap project is an impressive effort that includes a very large dataset of $184$ tree types~\cite{kumar2012leafsnap}. A mobile phone application is also developed to make the leaf classification system portable. Finally, the crop/weed image database~\cite{haug2014crop} is captured by a robot in the field, and used for classifying crop vs.~weed. Note that in this type of databases, normally only a single leaf is imaged and as a result, the challenging problem of leaf segmentation has been bypassed.

The second type of databases is for plant phenotyping, where it is important to capture plant images without interfering the growth of plants. Thus, non-destructive approaches are taken and the entire plant is imaged. The LSC database~\cite{scharr2014annotated} is the most similar one to our database. It captures a large set of RGB images for the Arabidopsis and Tobacco plants. The provided manual labels allow the evaluation of leaf segmentation and leaf counting. In comparison, our MSU-PID database utilizes four sensing modalities in the data capturing, each providing different aspects of plant appearance.
Our manual label also enable us to develop algorithm on additional applications such as leaf tracking and alignment.
